Analysis of the inference of ratings and rankings on Higher Order Networks with complex topologies

### 2025-09-03 draft/draft.tex
progress

With each metric, a 1-cochain is defined as
$$
f_{ij}
=
\frac{1}{2}(m_{ij}+m_{ji})
$$
Moreover, in order to test the inference method, two types of ground-truth 1-cochains are also defined.
Namely, the rank-based 1-cochain $f_{ij}=\frac{1}{2}(i-j)$ and the tournament point 1-cochain $f_{ij}=\frac{1}{2}(\pi_j-\pi_i)$.
Note, $f_{ij}=-f_{ji}$ holds by definition.
These 1-cochains $f$ define a fully connected network or graph, since all pairs of teams play two matches against each other in each league.
Each of these fully connected graphs of $N=n+1$ nodes is promoted to a simplicial complex compose of 0-simplices labeled by $i$, 1-simplices labeled by $ij$ and 2-simplices labeled by $ijk$ where $i,j,k$ are different elements in $\{0,1,2,...,n\}$.

>>>>

\subsection{Definition of 1-cochains}

With each metric, a 1-cochain is defined as
$$
f_{ij}
=
\frac{1}{2}(m_{ij}+m_{ji})
$$
Moreover, in order to test the inference method, two types of ground-truth 1-cochains are also defined.
Namely, the rank-based 1-cochain $f_{ij}=i-j$ and the tournament points based 1-cochain $f_{ij}=\pi_j-\pi_i$.
Note, $f_{ij}=-f_{ji}$ holds by definition.
These 1-cochains $f$ define a fully connected network or graph since, as already mentioned, all pairs of teams play two matches against each other in each league.
Each of these fully connected graphs of $N=n+1$ nodes is promoted to a simplicial complex composed of 0-simplices labeled by $i$, 1-simplices labeled by $ij$ and 2-simplices labeled by $ijk$ where $i,j$ and $k$ run over all choices in $\{0,1,2,...,n\}$ such that $i<j$ or $i<j<k$, depending on the case.
